Species persistence under climate and fishing

### 2014-02-01 Writing/MS.tex
Added a few details to MPA section, fixes #19

We also examined frequently recommended management approaches: harvest thresholds and MPAs and whether these strategies would work to ensure species persistence. We found these two management strategies to both increase the population's biomass at equilibrium and improved its ability to persist. Protected areas have been advanced as a way to help organisms keep pace with range shifts, as well as to ameliorate anthropogenic disturbances like harvesting and habitat fragmentation\citep{Lawleretal2010, Hannahetal2007,Botsfordetal2001, Gaylordetal2005, HastingsBotsford2003,Thomasetal2012}. Our results, that spatial management increased the maximum harvesting rate at which the population could survive, corroborate these previous findings. Harvesting thresholds are already widely implemented in fisheries management, and we found that this management tactic alleviates interactions between the two stressors.   While the management strategies only change harvesting practices and do not directly address the effects of climate change, understanding how they ameliorate synergistic affects between harvesting and range shifts will help to better implement harvesting rules and place protected areas.

>>>>

We also examined frequently recommended management approaches: harvest thresholds and MPAs and whether these strategies would work to ensure species persistence. We found these two management strategies to both increase the population's biomass at equilibrium and improved its ability to persist. Protected areas have been advanced as a way to help organisms keep pace with range shifts, as well as to ameliorate anthropogenic disturbances like harvesting and habitat fragmentation \citep{Lawleretal2010, Hannahetal2007,Botsfordetal2001, Gaylordetal2005, HastingsBotsford2003,Thomasetal2012}. Our results, that spatial management increased the maximum harvesting rate at which the population could survive, support the idea that MPAs could be used to reduce the impact of harvesting. However we did not find any evidence that MPAs increased the climate velocity under which the population could persist. The second management approach we investigated, harvesting thresholds, are already widely implemented in fisheries management, and we found that this management tactic alleviates interactions between the two stressors.   While the management strategies only change harvesting practices and do not directly address the effects of climate change, understanding how they ameliorate synergistic affects between harvesting and range shifts will help to better implement harvesting rules and place protected areas.
